\documentclass[12pt,letterpaper,boxed]{hmcpset}
\usepackage{float}
\restylefloat{figure}
\usepackage{graphicx}
\usepackage{amsmath}


\name{Lujia Zhang}
\class{CSSE 477}
\mailbox{CM 1405}
\assignment{Paper Review 4}

\begin{document}

\begin{problem}[Please review the attached paper by critically summarizing it in your own words.]
\end{problem}
Even though Agile development is popular among software industry, software intensive system developing companies such as automobiles, telecommunications, finance and medical companies still doubt about Agile approach. On the other hand, Agile supporters think software architectural design has little value since design should change throughout sprints and refactor. \newline
Unlike software architecture, Agile method doesn't plan too much in advance, it adapts design as development is happening. Finding a balance between software architecture and Agile is important.\newline
The disagreement and tension between architecture and Agile could be a fasle claim.\newline
By clarifying the semantics, it shows there isn't much distinction between design and architecture. Project context is what influenct architectural activity. Large and complicated projects require significant architectural effort. Agile method needs to suit the special demand. \newline
Architecture should be focused in the early beginning and architects need experience as both architectus reloadus and architectus oryzus. \newline
Software developers are equally important in successfully combining agile and architecture approaches because it’s up to the development team how to use various architectural artifacts and documents.\newline
Knowing the most appropriate time for key architectural decisions is important. Nonfunctional requirements can be ignored. \newline
There are six important things to be noticed.\newline
Understand the context, clearly define the architecture, define an architecture owner, exploit architecture with other teams and parties, only use important functionality to identify architectural issues, understand the timing to slow down architecture design, and keep track of unfinished and unresolved architectural issues.\newline






\end{document}